Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2016-01-04 src/tf-cutcell-comparison/tf-cutcell-comparison.tex
linear results no longer unstable, update cell area ratios for cut cell meshes

Using the centred linear scheme on the cut cell grid, numerical instability is generated by flow through small cells: when interpolating \(\phi\) onto faces, flux from a large cell into a small cell means that the downwind cell is given greater weighting, effectively making the scheme downwind-biased rather than upwind-biased.  The maximum Courant number is less than one in all of the advection tests, hence it is not the source of this instability.

@@

{$\Delta z$ (\si{\meter})} & \multicolumn{2}{c}{max/min cell area ratio} \\
 & {BTF} & {Cut cell} \\
\hline
500	& 1.01 &  999 \\
300	& 1.01 &  999 \\
250	& 1.01 &  999 \\
200	& 1.01 &  999 \\
150	& 1.01 &  999 \\
125	& 1.01 &  999 \\
100	& 1.01 &  999 \\
75	& 1.01 &  999 \\
50	& 1.01 &  999 \\
\hline
\end{tabular}
\end{table}

>>>>

@@

{$\Delta z$ (\si{\meter})} & \multicolumn{2}{c}{max/min cell area ratio} \\
 & {BTF} & {Cut cell} \\
\hline
500	& 1.01 &  1.68 \\
300	& 1.01 &  7.33 \\
250	& 1.01 &  5.44 \\
200	& 1.01 &  5.20 \\
150	& 1.01 &  10.0 \\
125	& 1.01 &  10.2 \\
100	& 1.01 &  10.0 \\
75	& 1.01 &  10.3 \\
50	& 1.01 &  10.4 \\
\hline
\end{tabular}
\end{table}
